Supplement 1

### 2020-09-09 paper/supplement-1.Rmd
add bibliography for supp1

---
title: Supplement 1
output: html_document
---

@@

Data MAR could arise if players' body mass measurements were taken with a
weighing scale that produced more missing values when placed on soft carpet,
rather than hard tiles, in the team change room. If surface type was recorded,
data would be MAR, because the missingness is related the surface, but not
related to the value of body mass itself. (ref:
https://stefvanbuuren.name/fimd/sec-MCAR.html).

@@

>>>>

---
title: Supplement 1
output: html_document
bibliography: supp1.bib
---

@@

Data MAR could arise if players' body mass measurements were taken with a
weighing scale that produced more missing values when placed on soft carpet,
rather than hard tiles, in the team change room. If surface type was recorded,
data would be MAR, because the missingness is related the surface, but not
related to the value of body mass itself [@VanBuuren2012].

@@

# References
